Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd

1. 'filtered permeability', where measures such as point closures or contraflow cycle lanes are used to design street networks in which routes for cyclists are faster and more direct than routes for drivers, e.g. as [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets]
2. banning cars and to pedestrianise streets, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020]
3. the reallocation of one or more lanes on wide roads to create pop-up cycleways and pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

>>>>

1. Measures such as point closures or contraflow cycle lanes, which can be used to promote 'filtered permeability', a strategy in which street networks are redesigned so that routes for cyclists are faster and more direct than routes for drivers. An example of this is  [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets].
2. Measures to close roads entirely to motor traffic or to particular classes of vehicle, either permanently or at certain times of day, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020].
3. Measures to reallocate space on wide roads to create new cycleways or to widen pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->
